Mungbean Powdery Mildew Spray Timing

### 2019-11-03 Cluster Timing/MB_PM_data.Rmd
Uses Paul's new csv file and adds third spray date clusters

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(skimr)
mb <- read_csv("slim-mungbean-powdery_mildew.csv")
```

@@

```{r mutate-filter}
mb <-
  mb %>%
  select(-c(fungicide_application_3:fungicide_application_7)) %>%
  mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
  mutate_at(vars(starts_with("fungicide_application_")), dmy) %>%
  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
  mutate(fungicide_timing_2 = fungicide_application_2 - first_sign_disease) %>%
  filter(!is.na(grain_yield.t.ha.))
```

@@

```{r second-spray-hist}
ggplot(filter(mb, !is.na(fungicide_timing_2)),
       aes(x = as.numeric(fungicide_timing_2))) +
   geom_histogram(bins = 50, fill = "grey") +
   geom_vline(linetype = 2,
              xintercept = 14,
              colour = "red") +
   xlab("Days from first sign") +
   ggtitle("Second Application",
           subtitle = "Line at 14 days after first sign") +
   theme_bw()
```

@@

```{r cluster}
mb <-
  mb %>%
  mutate(
    cluster_1 = case_when(
      fungicide_timing_1 < 0 ~ "Early",
      fungicide_timing_1 >= 0 &
        fungicide_timing_1 < 3 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>%
  mutate(
    cluster_2 = case_when(
      fungicide_timing_2 < 13 ~ "Early",
      fungicide_timing_2 >= 13 &
        fungicide_timing_2 < 17 ~ "Recommended",
      TRUE ~ "Late"
    )
  )
```

@@

```{r hist-clust2}
ggplot(filter(mb, !is.na(fungicide_timing_2)),
       aes(x = as.numeric(fungicide_timing_2))) +
  geom_histogram(bins = 50, aes(fill = cluster_2)) +
  scale_fill_viridis_d("Cluster") +
  geom_vline(linetype = 2,
             xintercept = 14,
             colour = "red") +
  xlab("Days from first sign") +
  ggtitle("Second Application",
          subtitle = "Line at 14 days after first sign") +
  theme_bw()
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(skimr)
mb <- read_csv("slim_PM_dat.csv")
```

@@

```{r mutate-filter}
mb <-
  mb %>%
  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
  mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
  mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
  filter(!is.na(grain_yield.t.ha)) %>% 
  filter(!is.na(PM_final_severity))
```

@@

```{r second-spray-hist}
ggplot(filter(mb, !is.na(fungicide_timing_2)),
       aes(x = as.numeric(fungicide_timing_2))) +
   geom_histogram(bins = 50, fill = "grey") +
   geom_vline(linetype = 2,
              xintercept = 14,
              colour = "red") +
   xlab("Days from first sign") +
   ggtitle("Second Application",
           subtitle = "Line at 14 days after first spray") +
   theme_bw()
```

@@

## Third spray

```{r third-spray-hist}
ggplot(filter(mb, !is.na(fungicide_timing_3)),
       aes(x = as.numeric(fungicide_timing_3))) +
   geom_histogram(bins = 50, fill = "grey") +
   geom_vline(linetype = 2,
              xintercept = 14,
              colour = "red") +
   xlab("Days from first sign") +
   ggtitle("Second Application",
           subtitle = "Line at 14 days after second spray") +
   theme_bw()
```

```{r cluster}
mb <-
  mb %>%
  mutate(
    cluster_1 = case_when(
      fungicide_timing_1 < 0 ~ "Early",
      fungicide_timing_1 >= 0 &
        fungicide_timing_1 < 4 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>%
  mutate(
    cluster_2 = case_when(
      fungicide_timing_2 < 13 ~ "Early",
      fungicide_timing_2 >= 13 &
        fungicide_timing_2 < 17 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>% 
  mutate(
    cluster_3 = case_when(
      fungicide_timing_3 < 14 ~ "Early",
      TRUE ~ "Recommended"
    )
  )
```

@@

The APVMA permit allows for a second spray not sooner than 14 days after the first.

```{r hist-clust2}
ggplot(filter(mb, !is.na(fungicide_timing_2)),
       aes(x = as.numeric(fungicide_timing_2))) +
  geom_histogram(bins = 50, aes(fill = cluster_2)) +
  scale_fill_viridis_d("Cluster") +
  geom_vline(linetype = 2,
             xintercept = 14,
             colour = "red") +
  xlab("Days from first application") +
  ggtitle("Second Application",
          subtitle = "Line at 14 days after first application") +
  theme_bw()
```

@@

## Third spray

The APVMA permit allows for a second spray not sooner than 14 days after the first.

```{r hist-clust3}
ggplot(filter(mb, !is.na(fungicide_timing_3)),
       aes(x = as.numeric(fungicide_timing_3))) +
  geom_histogram(bins = 50, aes(fill = cluster_3)) +
  scale_fill_viridis_d("Cluster") +
  geom_vline(linetype = 2,
             xintercept = 14,
             colour = "red") +
  xlab("Days from second sign") +
  ggtitle("Second Application",
          subtitle = "Line at 14 days after second application") +
  theme_bw()
```
